---
title: "Council Snapshots"
subtitle: "District `r params$coun_dist`: Week of `r params$pretty_week`"
# author: "Data Operations Unit"
date: "Generated on: `r councildown::pretty_date()`"
output:
  bookdown::word_document2:
    toc: yes
    reference_docx: assets/word_theme.docx
  # bookdown::pdf_document2: default
  # councildown::council_pdf:
  #   latex_engine: xelatex
  # councildown::council_html: default
compact-title: true
fontsize: 11pt
subparagraph: yes
always_allow_html: yes
params:
  week: NA
  coun_dist: NA
  pretty_week: NA
header-includes:
  - \usepackage{lscape}
---


```{r include = FALSE}
library(ggplot2)
# library(councildown)

knitr::knit_hooks$set(embed = councildown::hook_pdfembed)
knitr::opts_chunk$set(echo = FALSE, embed = TRUE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r}
week <- params$week
coun_dist <- params$coun_dist
```

```{r results = "hide"}
library(shiny)
library(shinydashboard)
library(tibble)
library(ggplot2)
library(dplyr)
library(lubridate)
library(stringr)
library(leaflet)
library(stringr)
library(purrr)
library(sf)

utils <- list.files(path = "util", pattern = "\\.(R|r)$", full.names = TRUE)
lapply(utils, source)

current_week <- tbl(snapshots_db, "sr_top_10_week_district_closed") %>%
  group_by(coun_dist) %>%
  summarize(week = max(week)) %>%
  ungroup() %>%
  summarize(week = min(week)) %>%
  pull()

dists <- tbl(snapshots_db, "council_districts") %>%
  collect_geo()

Fmt <- function(x) UseMethod("Fmt")
Fmt.difftime <- function(x) {
  units(x) <- "secs"
  x <- unclass(x)
  NextMethod()
}
Fmt.default <- function(x) {
  y <- abs(x)
  
  # if(is.na(y)){ return("Ongoing as of last update")}
  
  sprintf("%02d hours %02d minutes",
          y %/% 3600,  # hours
          y %% 3600 %/% 60) # minutes
}

```


# 311 Service Requests ^[Note: 311 Service Requests data is representative of the population that makes a service request. Generalizations can't be made for the entire city or district population.]

## Submitted Service Requests

```{r}
dist_week <- tbl(snapshots_db, "sr_ind_top_10_week_district") %>%
  filter(coun_dist == local(coun_dist),
         week == local(week)) %>%
  collect_geo()
```

```{r}
dist_week %>%
  count(complaint_type) %>%
  # wrap labels for prettiness
  mutate(complaint_type = tools::toTitleCase(tolower(complaint_type)) %>%
           str_wrap(15) %>%
           reorder(n)) %>%
  ggplot(aes(complaint_type, n, fill = complaint_type,
             text = paste(complaint_type, n, sep = "<br>"))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = "Complaint type",
       y = "Number of service requests") +
  councildown::scale_fill_nycc() +
  scale_x_discrete(labels = function(x) str_replace(x, "(^.*?\\n)(.*?)(\\n.*?)+$", "\\1\\2...")) +
  theme_bw()
```

```{r}
dat <- dist_week %>%
  as.data.frame()
pal <- colorFactor(councildown::nycc_pal()(length(unique(dat$complaint_type))),
                   reorder(count(dat, complaint_type)$complaint_type, count(dat, complaint_type)$n))
```

```{r}
map_data <- dist_week %>%
  mutate(lon = st_coordinates(.)[,1], lat = st_coordinates(.)[,2]) %>%
  as.data.frame() %>%
  group_by(lon, lat, complaint_type) %>%
  summarize(n = n(), created_date = paste0(created_date, collapse = "<br>"),
            incident_address = paste0(unique(incident_address), collapse = "<br>")) %>%
  st_as_sf(coords = c("lon", "lat"), crs = st_crs(dist_week))
```

```{r screenshot.force = TRUE}
bbox <- as.numeric(st_bbox(map_data))

leaflet(map_data) %>%
  councildown::addCouncilStyle() %>%
  clearGroup("complaints") %>%
  addCircleMarkers(radius = 4, weight = 15, fillOpacity = .8, opacity = 0,
                   fillColor = ~pal(complaint_type)) %>% 
  fitBounds(bbox[1], bbox[2], bbox[3], bbox[4])
```


```{r}
dist_ytd <- tbl(snapshots_db, "sr_top_10_ytd_district") %>%
  filter(coun_dist == local(coun_dist)) %>%
  select(-locations) %>%
  collect()
```

```{r}
dist_ytd %>%
  mutate(complaint_type = tools::toTitleCase(tolower(complaint_type)) %>%
           str_wrap(15) %>%
           reorder(n_tot)) %>%
  ggplot(aes(complaint_type, n_tot, fill = as.numeric(complaint_type),
             text = paste(complaint_type, n_tot, sep = "<br>"))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_fill_gradient(low = "#2F56A6", high = "#23417D") +
  scale_x_discrete(labels = function(x) str_replace(x, "(^.*?\\n)(.*?)(\\n.*?)+$", "\\1\\2...")) +
  labs(x = "Complaint type",
       y = "Number of service requests") +
  theme_bw()
```

```{r}
dist_all <- tbl(snapshots_db, "sr_week_district") %>%
  filter(coun_dist == local(coun_dist)) %>%
  select(-locations)
```

```{r}
dist_all %>%
  filter(week <= local(current_week)) %>%
  group_by(week) %>%
  summarize(n = sum(n)) %>%
  collect() %>%
  mutate(date = floor_date(ymd("2019-01-01")+(7*(week-1)), unit = "week") + 1) %>%
  ggplot(aes(date, n,
             text = paste0("Week of ", format(date, format = "%b %e"), ": ", n, " service requests"), group = 1, group = 1)) +
  geom_point(color = "#23417D") +
  geom_line(color = "#23417D") +
  labs(x = "Week",
       y = "Number of service requests") +
  theme_bw()
```


```{r}
setProgress(.2)
```


## Closed Service Requests

```{r}
dist_week <- tbl(snapshots_db, "sr_ind_top_10_week_district_closed") %>%
  filter(coun_dist == local(coun_dist),
         week == local(week)) %>%
  collect_geo()
```

```{r}
dist_week %>%
  count(complaint_type) %>%
  # wrap labels for prettiness
  mutate(complaint_type = tools::toTitleCase(tolower(complaint_type)) %>%
           str_wrap(15) %>%
           reorder(n)) %>%
  ggplot(aes(complaint_type, n, fill = complaint_type,
             text = paste(complaint_type, n, sep = "<br>"))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = "Complaint type",
       y = "Number of service requests") +
  councildown::scale_fill_nycc() +
  scale_x_discrete(labels = function(x) str_replace(x, "(^.*?\\n)(.*?)(\\n.*?)+$", "\\1\\2...")) +
 theme_bw()
```

```{r}
dat <- dist_week %>%
  as.data.frame()
pal <- colorFactor(councildown::nycc_pal()(length(unique(dat$complaint_type))),
                   reorder(count(dat, complaint_type)$complaint_type, count(dat, complaint_type)$n))
```

```{r}
map_data <- dist_week %>%
  mutate(lon = st_coordinates(.)[,1], lat = st_coordinates(.)[,2]) %>%
  as.data.frame() %>%
  group_by(lon, lat, complaint_type) %>%
  summarize(n = n(), created_date = paste0(created_date, collapse = "<br>"),
            incident_address = paste0(unique(incident_address), collapse = "<br>")) %>%
  st_as_sf(coords = c("lon", "lat"), crs = st_crs(dist_week))
```

```{r screenshot.force = TRUE}
bbox <- as.numeric(st_bbox(map_data))

leaflet(map_data) %>%
  councildown::addCouncilStyle() %>%
  clearGroup("complaints") %>%
  addCircleMarkers(radius = 4, weight = 15, fillOpacity = .8, opacity = 0,
                   fillColor = ~pal(complaint_type)) %>% 
  fitBounds(bbox[1], bbox[2], bbox[3], bbox[4])
```


```{r}
dist_ytd <- tbl(snapshots_db, "sr_top_10_ytd_district_closed") %>%
  filter(coun_dist == local(coun_dist)) %>%
  select(-locations) %>%
  collect()
```

```{r}
dist_ytd %>%
  mutate(complaint_type = tools::toTitleCase(tolower(complaint_type)) %>%
           str_wrap(15) %>%
           reorder(n_tot)) %>%
  ggplot(aes(complaint_type, n_tot, fill = as.numeric(complaint_type),
             text = paste(complaint_type, n_tot, sep = "<br>"))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_fill_gradient(low = "#2F56A6", high = "#23417D") +
  scale_x_discrete(labels = function(x) str_replace(x, "(^.*?\\n)(.*?)(\\n.*?)+$", "\\1\\2...")) +
  labs(x = "Complaint type",
       y = "Number of service requests") +
  theme_bw()
```

```{r}
dist_all <- tbl(snapshots_db, "sr_week_district_closed") %>%
  filter(coun_dist == local(coun_dist)) %>%
  select(-locations)
```

```{r}
dist_all %>%
  filter(week <= local(current_week)) %>%
  group_by(week) %>%
  summarize(n = sum(n)) %>%
  collect() %>%
  mutate(date = floor_date(ymd("2019-01-01")+(7*(week-1)), unit = "week") + 1) %>%
  ggplot(aes(date, n,
             text = paste0("Week of ", format(date, format = "%b %e"), ": ", n, " service requests"), group = 1, group = 1)) +
  geom_point(color = "#23417D") +
  geom_line(color = "#23417D") +
  labs(x = "Week",
       y = "Number of service requests") +
  theme_bw()
```

```{r}
setProgress(.4)
```


# OEM Incidents^[Note: Emergency Response Incidents are emergencies that NYCEM responded to. There are 13 emergency categories to date: Administration, Aviation, Fire, HazMat, Law Enforcement, Marine, Medical, Rescue, Structural, Transportation, Utility, Weather and Other.]

```{r}
oem_week_dist <- tbl(snapshots_db, "emergency_response") %>%
  filter(date_part("week", creation_date) == local(week)) %>%
  collect_geo() %>%
  st_join(dists) %>%
  rename(coun_dist_dat = coun_dist) %>% 
  filter(coun_dist_dat == coun_dist) %>%
  mutate(duration = closed_date - creation_date,
         duration_pretty = ifelse(is.na(duration), "Ongoing as of last update", Fmt(duration)))
```

```{r screenshot.force = TRUE}

if (nrow(oem_week_dist) > 0){
  bbox <- as.numeric(st_bbox(oem_week_dist))
  
  oem_week_dist %>% 
    leaflet() %>%
    councildown::addCouncilStyle() %>% 
    addCircleMarkers(radius = ~ifelse(is.na(duration), 5, 25*sqrt(as.double(duration)/max(as.double(duration)))),
                     popup = ~paste(incident_type, location, paste(creation_date, closed_date, sep = " - "), duration_pretty, sep = "<br>"),
                     fillOpacity = .8, fillColor = ~ifelse(is.na(closed_date), "#D05D4E","#2F56A6"), opacity = 0, weight = 15,
                     group = "oem_incidents") %>%
    clearControls() %>%
    flyToBounds(bbox[1], bbox[2], bbox[3], bbox[4], options = list(duration = .25))
}
```

```{r}
if (nrow(oem_week_dist) > 0){
  oem_week_dist %>%
    as.data.frame() %>%
    select(incident_type, location, creation_date, closed_date) %>%
    knitr::kable(col.names = c('Incident','Location', 'Start Time', 'Closed'))
}
```

`r if (nrow(oem_week_dist) == 0) {"No emergency incidents."}`

```{r}
setProgress(.6)
```


# HPD Vacate Orders

## Issued Vacate Orders


```{r include=FALSE}
issued_week_dist <- tbl(snapshots_db, "vacate_orders") %>%
  filter(council_district == local(coun_dist),
         date_part("week", vacate_effective_date) == local(week)) %>%
  mutate(address = paste(number, street)) %>%
  collect_geo()
```


```{r screenshot.force = TRUE}
if (nrow(issued_week_dist) > 0) {
  bbox <- as.numeric(st_bbox(issued_week_dist))
  
  issued_week_dist %>% 
    leaflet() %>%
    councildown::addCouncilStyle() %>%
    addCircleMarkers(radius = 5,
                     fillOpacity = .8, fillColor = "#2F56A6", opacity = 0, weight = 15,
                     popup = ~paste(address, primary_vacate_reason, vacate_effective_date, sep = "<br>"),
                     group = "issued") %>%
    clearControls() %>%
    flyToBounds(bbox[1], bbox[2], bbox[3], bbox[4], options = list(duration = .25))
}
```


```{r}
if (nrow(issued_week_dist) > 0) {
  issued_week_dist %>%
    as.data.frame() %>%
    select(address, primary_vacate_reason, vacate_type, vacate_effective_date, number_of_vacated_units) %>%
    knitr::kable(col.names = c('Address','Vacate Reason','Type', 'Effective Date', 'Units Vacated'))
}
```

`r if (nrow(issued_week_dist) == 0) {"No issued vacate orders."}`

```{r}
setProgress(.8)
```


## Rescinded Vacate Orders

```{r include = FALSE}
rescinded_week_dist <- tbl(snapshots_db, "vacate_orders") %>%
  filter(council_district == local(coun_dist),
         date_part("week", rescind_date) == local(week)) %>%
  mutate(address = paste(number, street)) %>%
  collect_geo()
```


```{r screenshot.force = TRUE}
if (nrow(rescinded_week_dist) > 0) {
  bbox <- as.numeric(st_bbox(rescinded_week_dist))
  rescinded_week_dist %>% 
    leaflet() %>%
    councildown::addCouncilStyle() %>%
    addCircleMarkers(radius = 5,
                     fillOpacity = .8, fillColor = "#2F56A6", opacity = 0, weight = 15,
                     popup = ~paste(address, primary_vacate_reason, vacate_effective_date, sep = "<br>"),
                     group = "rescinded") %>%
    clearControls() %>%
    flyToBounds(bbox[1], bbox[2], bbox[3], bbox[4], options = list(duration = .25))
}
```


```{r}
if (nrow(rescinded_week_dist) > 0) {
  rescinded_week_dist %>%
    as.data.frame() %>%
    select(address, primary_vacate_reason, vacate_type, vacate_effective_date, number_of_vacated_units) %>%
    knitr::kable(col.names = c('Address','Vacate Reason','Type', 'Effective Date', 'Units Vacated'))
}
```

`r if (nrow(rescinded_week_dist) == 0) {"No rescinded vacate orders."}`


# Sources
**311 Service Requests**, NYC OpenData: 311, DoITT, https://data.cityofnewyork.us/Social-Services/311-Service-Requests-from-2010-to-Present/erm2-nwe9

**Emergency Response Incidents**, NYC OpenData: NYCEM, https://data.cityofnewyork.us/Public-Safety/Emergency-Response-Incidents/pasr-j7fb

**Order to Repair/Vacate Orders**, NYC OpenData: HPD, https://data.cityofnewyork.us/Housing-Development/Order-to-Repair-Vacate-Orders/tb8q-a3ar
```{r}
setProgress(.9)
```

